Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support).

### 2017-02-06 csf-2017/paper.tex
added first high-level motivation

\section{Introduction}
\label{sec:introduction}
%%% a)
% Current low-level protection coarse grained memory protection or
% properties of high-level languages are not really enforced?

>>>>

\section{Introduction}
\label{sec:introduction}
\todo[inline]{See the latex comments for the next paragraphs!}
% Possible high-level intros:
% 1) Security guarantees vs obstacles / arms race
Security on processors is today subject to an arms race between
processor manufacturers and hackers. On the hacker side, a constant
effort is put into exploiting current processor designs and
circumventing the security measures set in place to prevent known
exploits. On the processor manufacturer side, new security measures
are put in place to prevent new exploits. The arms race would come to
a grinding halt if the security meassures provided more than obstacles
and actually provided low-level security guarantees. One kind of
low-level machines that provide low-level security is a capability machine.

% 2) Memory access-control

% 3) Fully abstract compilation

%%% a)
% Current low-level protection coarse grained memory protection or
% properties of high-level languages are not really enforced?
